\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-20 response_to_referee_v1.tex

	\textbf{Response:} Thanks for the comment. In fact,
\begin{equation*}
\begin{aligned}
\sigma^2 &= \|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2\\
 &=\tau^2\|A(A^\dagger b - \widehat x_{\rm spgl1})\|^2 + 2\tau\|A(A^\dagger b - \widehat x_{\rm spgl1})\|\|A(\widehat x_{\rm spgl1} - b\| + \|A(\widehat x_{\rm spgl1} - b\|^2
\end{aligned}
\end{equation*}
which is a quadratic function in $\tau$. It is easy to calculate $\tau$.

	\item  \textit{\textbf{Reviewer:}} \textit{Numerical results: As far as I see, Algorithm 3 does not require to find a completely feasible initial point ($x_0\in F$) but just in C ($x_0\in C$). I did not find any statement about how the initial point is chosen for ESQM$_{\rm ls}$. In principle, SPGL1 and Slater point are not needed. Therefore, it is not fair to say that FPA is faster since the sum of the iteration time plus the required initialization exceeds the CPU time of ESQM$_{\rm ls}$. Would it be any other cheaper way to compute $x_0$?}

	\textbf{Response:} Thanks for the comment. We choose different initial point for comparison in problem (6.1). When the initial point
$x^0 = (0, 0, \cdots, 0)$, we have the results in Table 1; When the initial point $x^0$ is given as in (6.6), we have the results in Table 2. Since the problem is non-convex, we can see from the results that the initial value has great influence on the efficiency of the algorithms. Although ESQM$_{\rm ls}$ is faster than FPA$_{\rm retract}$ when the initial value is zero, FPA$_{\rm retract}$ is faster than ESQM$_{\rm ls}$ when the initial point $x^0$ is given as in (6.6).

\begin{table}[H]
\caption{Computational results for problem (6.2) with initial point $x^0 = (0, 0, \cdots, 0)$}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ } & \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.50 &   3.11 &   9.79 &  22.95 &  43.99\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.38 &   7.54 &  15.69 &  28.50 &  50.25\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  14.09 &  62.33 & 139.27 & 241.40 & 388.70\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   4.92 &  25.75 &  59.09 & 102.56 & 170.23\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.42 &  21.80 &  49.89 &  86.37 & 142.02\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.36 &  59.88 & 135.25 & 236.76 & 378.49\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&   1638 &   1847 &   1885 &   1883 &   1957\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    759 &   1025 &   1075 &   1080 &   1158\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    767 &    913 &    946 &    941 &    991\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2439 &   2579 &   2618 &   2620 &   2670\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.060 &  0.051 &  0.055 &  0.055 &  0.046\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -1.72e-04 & -2.10e-04 & -1.53e-04 & -1.37e-04 & -1.26e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& 1.69e-15 & 1.35e-15 & 2.79e-16 & -7.54e-16 & -1.42e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.21e-10 & 1.22e-10 & 1.12e-10 & 1.10e-10 & 1.11e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 1.06e-10 & 9.98e-11 & 9.32e-11 & 9.36e-11 & 9.10e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.01e-10 & 9.93e-11 & 9.77e-11 & 9.47e-11 & 9.60e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

\begin{table}[H]
\caption{Computational results for problem (6.2) with initial point $x^0$ is given as in (6.6)}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.47 &   3.05 &   9.83 &  23.25 &  44.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.59 &   7.35 &  15.20 &  30.17 &  48.54\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.40 &  12.30 &  37.94 &  56.91 &  97.89\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.43 &  23.38 &  61.11 & 104.34 & 173.99\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.64 &  20.41 &  51.46 &  88.36 & 146.46\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.25 &  58.83 & 136.92 & 239.48 & 382.51\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    420 &    368 &    520 &    444 &    493\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    893 &    937 &   1113 &   1099 &   1186\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    839 &    863 &    977 &    963 &   1025\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2508 &   2550 &   2653 &   2650 &   2702\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.061 &  0.045 &  0.066 &  0.051 &  0.054\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.72e-04 & -2.20e-04 & -1.41e-04 & -1.19e-04 & -1.30e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.86e-16 & 2.98e-16 & 1.85e-15 & -5.27e-16 & -1.31e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.08e-10 & 1.15e-10 & 1.01e-10 & 1.09e-10 & 1.05e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 9.49e-11 & 9.50e-11 & 8.90e-11 & 9.60e-11 & 9.95e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 9.35e-11 & 9.91e-11 & 9.14e-11 & 9.44e-11 & 9.34e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

@@

	\item \textit{\textbf{Reviewer:}} \textit{ f) Subproblem (4.6): Should it be $\sigma^x$?}

    \textbf{Response:} Thanks for the comment. It should be $\sigma$ in subproblem (4.6). Indeed, in view of Lemma 4.1(iv), one can see that the inequality constraint in (4.6) is the same as
    \[
    \ell^{x^k}(Ax^k - b) + \langle A^T\nabla \ell^{x^k}(Ax^k - b),x-x^k\rangle \le \tilde \sigma^{x^k}.
    \]

	\item \textit{\textbf{Reviewer:}} \textit{ g) Please compare the algorithms with the method presented in [42], by the third author.}

    \textbf{Response:} Thanks for the comment. We compare the algorithms with SCP presented in [42] on solving problem (6.4):
    \begin{equation}\label{pr1}
       \begin{array}{rl}
        \min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\| \\\\
        {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
       \end{array}
     \end{equation}
    Then, we have the results in Table 3.

### 2022-04-20 SQP+Retract_response_1.tex
Modified the second example and update the results

We next present the parameters, initial points and termination criteria used in our numerical experiments. Solution approaches for the subproblems involved are outlined in the appendix. All numerical experiments are performed in MATLAB R2019b on a 64-bit PC with an Intel(R)Core(TM) i7-6700 CPU (3.40GHz) and 32GB of RAM.

@@

{\color{red}We compare Algorithm~\ref{SQP_retract2} and Algorithm~\ref{ESQM} on solving random instances of \eqref{E4}. Specifically, we generate two matrices $A_1\in \R^{p\times n}$ and $A_2\in \R^{p\times n}$ with i.i.d standard Gaussian entries, and let
\begin{equation}
A := \left[ \begin{matrix}
A_1 & -A_2\\
A_2 & A_1
\end{matrix} \right]
\end{equation}
 then normalize each column of $A$. Next, we generate two vectors $u_1\in\R^k$ and $u_2\in\R^k$ with i.i.d standard Gaussian entries. We choose an index set $I$ of size $k$ at random and define the sparse original signal $\xorig\in \R^{n\times 2}$ by setting $\xorig(I,:) = [ u_1, u_2 ]$ and $\xorig(\bar{I},:) = 0$. We then let $b = A\xorig + 0.005\hat{\epsilon}$ with $\hat{\epsilon}_{i,j}$ independently following the Cauchy$(0, 1)$ distribution, $i=1, 2, \cdots n$, $j = 1, 2$, i.e., $\hat{\epsilon}_{i,j} = \tan(\pi(\widetilde{\epsilon}_{i,j} - \frac{1}{2}))$, where $\widetilde{\epsilon}_{\cdot, 1}\in\R^p$ and $\widetilde{\epsilon}_{\cdot, 2}\in\R^p$ are two random vectors with i.i.d entries uniformly chosen in $[0, 1]$. Finally, we set $\overline{\sigma} = 1.2\|0.005\hat{\epsilon}\|_{LL_2,\gamma}$ with $\gamma = 0.05$.}

@@

In our numerical experiments, we let $\mu =0.95$, $j = 2$, $\gamma = 0.05$, $(p,n,k) = (360i,1280i,60i)$ with $i\in \{2, 4, 6, 8, 10\}$. For each $i$, we generate 20 random instances as described above. The computational results averaged over the $20$ random instances are shown in Table~\ref{table2}. In the table, Algorithm~\ref{SQP_retract2} is denoted by FPA$_{\rm retract}$, Algorithm~\ref{ESQM} with different $\delta$ is denoted by ESQM$_{\rm ls}$ with the $\delta$ specified, and recall that SPGL1 is the algorithm used for obtaining initial points for FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ by solving the auxiliary problem~\eqref{SPGL1nonconvexL1}. As before, we present the time for performing QR decomposition on $A^T$ (denoted by QR), the time for computing $A^\dagger b$ given the QR factorization of $A^T$ (denoted by Slater), the CPU time of algorithms (CPU time),\footnote{The reported CPU times of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ do not include the time for generating $\xfeasss$ and $x^0$.} the number of iterations (denoted by Iter), the recovery errors $\text{RecErr} := \frac{\|x^* - \xorig\|}{\max\{1, \|\xorig\|\}}$ and the residuals ${\rm Residual} := \frac{\|Ax^* - b\|_{LL_2,\gamma} - \overline{\sigma} }{\overline{\sigma}}$, where $x^*$ is the approximate solution returned by the respective algorithm.

>>>>

We next present the parameters, initial points and termination criteria used in our numerical experiments. Solution approaches for the subproblems involved are outlined in the appendix. All numerical experiments are performed in MATLAB R2016a on a 64-bit PC with an Intel(R) Core(TM) i7-10710U CPU (@1.10GHz, 1.61GHz) and 16GB of RAM.

@@

{\color{blue}We compare Algorithm~\ref{SQP_retract2} and Algorithm~\ref{ESQM} on solving random instances of \eqref{E4}. Specifically, we generate two matrices $A_1\in \R^{p\times n}$ and $A_2\in \R^{p\times n}$ with i.i.d standard Gaussian entries, and let
\begin{equation}
A := \left[ \begin{matrix}
A_1 & -A_2\\
A_2 & A_1
\end{matrix} \right]
\end{equation}
 then normalize each column of $A$. Next, we generate two vectors $u_1\in\R^k$ and $u_2\in\R^k$ with i.i.d standard Gaussian entries. We choose an index set $I$ of size $k$ at random and define the sparse original signal $\xorig\in \R^{n\times 2}$ by setting $\xorig(I,:) = [ u_1, u_2 ]$ and $\xorig(\bar{I},:) = 0$. We then let $b = A\xorig + 0.005\hat{\epsilon}$ with $\hat{\epsilon}_{i,j}$ independently following the Cauchy$(0, 1)$ distribution, $i=1, 2, \cdots n$, $j = 1, 2$, i.e., $\hat{\epsilon}_{i,j} = \tan(\pi(\widetilde{\epsilon}_{i,j} - \frac{1}{2}))$, where $\widetilde{\epsilon}_{\cdot, 1}\in\R^p$ and $\widetilde{\epsilon}_{\cdot, 2}\in\R^p$ are two random vectors with i.i.d entries uniformly chosen in $[0, 1]$. Finally, we set $\overline{\sigma} = 1.2\|0.005\hat{\epsilon}\|_{LL_2,\gamma}$ with $\gamma = 0.05$.}

@@

In our numerical experiments, we let $\mu =0.95$, $j = 2$, $\gamma = 0.05$, {\color{blue} $(p,n,k) = (360i,1280i,60i)$ }with $i\in \{2, 4, 6, 8, 10\}$. For each $i$, we generate 20 random instances as described above. The computational results averaged over the $20$ random instances are shown in Table~\ref{table2}. In the table, Algorithm~\ref{SQP_retract2} is denoted by FPA$_{\rm retract}$, Algorithm~\ref{ESQM} with different $\delta$ is denoted by ESQM$_{\rm ls}$ with the $\delta$ specified, and recall that SPGL1 is the algorithm used for obtaining initial points for FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ by solving the auxiliary problem~\eqref{SPGL1nonconvexL1}. As before, we present the time for performing QR decomposition on $A^T$ (denoted by QR), the time for computing $A^\dagger b$ given the QR factorization of $A^T$ (denoted by Slater), the CPU time of algorithms (CPU time),\footnote{The reported CPU times of FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ do not include the time for generating $\xfeasss$ and $x^0$.} the number of iterations (denoted by Iter), the recovery errors $\text{RecErr} := \frac{\|x^* - \xorig\|}{\max\{1, \|\xorig\|\}}$ and the residuals ${\rm Residual} := \frac{\|Ax^* - b\|_{LL_2,\gamma} - \overline{\sigma} }{\overline{\sigma}}$, where $x^*$ is the approximate solution returned by the respective algorithm.
